### 2008-12-20 talk/ecoop2009/rainbow.tex
add the final version of the code

\subsection{Implementing Promotion}

@@

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval_abs(args):
    v0 = args[0]
    v1 = IntObj(0)
    a, b = v0, v1
    # hint(a, promote_class=True) implemented as follows:
    cls_a = a.__class__
    switch cls_a:
        IntObj:
            # hint(b, promote_class=True) needs no code
            v0 = IntObj(b.value < a.value)
            if v0.value:
                return a
            else:
                v0 = IntObj(0)
                v1 = args[0]
                a, b = v0, v1
                v0 = IntObj(b.value - a.value)
                return v0
        default: 
            continue_compilation(jitstate, cls_a)
\end{lstlisting}
\caption{Promotion step 2}
\label{fig:tlc-abs-promotion-2}
\end{center}
\end{figure}

@@

\anto{We should show the very final version of the code, with all instances virtualized}

>>>>

\subsection{Implementing Promotion}
\label{sec:implementing-promotion}

@@

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval_abs(args):
    v0 = args[0]
    v1 = IntObj(0)
    a, b = v0, v1
    # hint(a, promote_class=True) implemented as follows:
    cls_a = a.__class__
    switch cls_a:
        IntObj:
            # hint(b, promote_class=True) needs no code
            v0 = IntObj(b.value < a.value)
            cond = v0
            if cond.value:
                return a
            else:
                v0 = IntObj(0)
                v1 = args[0]
                a, b = v0, v1
                v0 = IntObj(b.value - a.value)
                return v0
        default: 
            continue_compilation(jitstate, cls_a)
\end{lstlisting}
\caption{Promotion step 2}
\label{fig:tlc-abs-promotion-2}
\end{center}
\end{figure}

@@

Figure~\ref{fig:tlc-abs-final} shows the final, fully optimized version of the
code, with all the instances virtualized and the unneeded temporary variables
removed.

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval_abs(args):
    a = args[0]
    cls_a = a.__class__
    switch cls_a:
        IntObj:
            # 0 is the constant "value" field of the virtualized IntObj(0)
            if 0 < a.value:
                return a
            else:
                return IntObj(0 - a.value)
        default: 
            continue_compilation(jitstate, cls_a)
\end{lstlisting}
\caption{Final optimized version of the \lstinline{abs} example}
\label{fig:tlc-abs-final}
\end{center}
\end{figure}
